\thetitle

### 2013-04-13 tfpie/tfpie.tex
Section labels.

\section{Introduction}

@@

\section{Background: the context at Northeastern}

At Northeastern, the College of Computer \& Information Science
requires a four course introductory sequence in the first year.  The
first semester features both a course on discrete mathematics as well
as an introduction to programming following the \emph{How to Design
  Programs} curriculum.  The second semester follows with a course on
object-oriented programming and one featuring formal reasoning about
programs, both on paper and with the ACL2 theorem prover.

@@

\section{A small shift of focus}

@@

\section{From principles to industrial languages}

@@

\section{Related work}

@@

\section{Experience and outlook}

>>>>

\section{Introduction}
\label{sec:intro}

@@

\section{Background: the context at Northeastern}
\label{sec:background}

At Northeastern, the College of Computer \& Information Science
requires a four course introductory sequence in the first year.  The
first semester features both a course on discrete mathematics as well
as an introduction to programming following the \emph{How to Design
  Programs} curriculum.  The second semester follows with a course on
object-oriented programming and one featuring formal reasoning about
programs, both on paper and with the ACL2 theorem
prover~\cite{dvanhorn:Kaufmann2000ComputerAided}.

@@

\section{A small shift of focus}
\label{sec:shift}

@@

\section{From principles to industrial languages}
\label{sec:industrial}

@@

\section{Related work}
\label{sec:related-work}

@@

\section{Experience and outlook}
\label{sec:conclusion}
